Linear Stochastic Approximation- Constant Step-Size and Iterate Averaging

### 2017-05-15 related.tex
updates

\paragraph{SGD for Linear Regression} As mentioned in \Cref{sec:intro}, we were motivated by the ``remarkable'' results obtained by \citet{bach}, where the authors analyse the performance of SGD for the problem of linear regression with quadratic loss. The problem class considered by them belongs to $\P_{\text{PSD},B}$ (see \Cref{def:pclass} ) and hence is weakly admissible with a uniform step-size choice. In order to produce a rate of $\frac{C}{t}$ (where $C>0$ is a problem independent constant) for the bias term \citet{bach} do not rely on admissibility, but instead use the fact that the MSE $\EE{\norm{\thh_t-\ts}^2_{A_P}}$ for the linear prediction problem is measured in the general quadratic norm induced by $A_P$ and the fact that the noise is `structured' i.e., the noise is bounded by $R\,A_P$ for some constant $R>0$. At the same time, the bias term decays at a rate $\frac{C'}{t^2}$, where the constant $C'$ contains the factor $(\theta_0-\ts)^\top A^{-1}_P (\theta_0-\ts)$ and is dependent on the condition number.
\paragraph{General LSA:} Analysis of LSA with CS-PR goes back to the work by \citet{polyak-judisky}, wherein they considered the additive noise setting i.e., $A_t=A$ for some deterministic Hurwitz matrix $A\in \R^{\dcd}$.
\paragraph{Our Results:} A key improvement in this paper is that we consider the `multiplicative' noise case, i.e., $A_t$ is a random matrix. To tackle the multiplicative noise we use newer analysis introduced by \citet{bach}. However, since the general LSA setting does not enjoy special structures of the SGD setting, we make use of Jordan decomposition and similarity transformations in a critical way to prove our results.
\subsection{Reinforcement Learning}
\paragraph{Notation:} We are presented with data in the form of an $i.i.d$ sequence $(\phi_t,\phi'_t,r_t)\in \R^d\times\R^d\times \R$. Let $\gamma \in (0,1)$ be a fixed constant, we define $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$. In what follows, $\mu_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\mu_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\mu_t>0$ is known as \emph{off-policy}.}.

@@

@@

The \emph{temporal difference} learning algorithm or simply known as TD(0), is the most basic of the class of TD algorithms. An important shortcoming of TD(0) was its instability in the \emph{off-policy} case, and was successfully mitigated by the \emph{gradient temporal difference} learing GTD \cite{gtd2}. The GTD was first proposed by \citet{gtd} and its variants namely GTD2 and TDC were proposed later by \citet{gtd2}. However, the initial convergence analysis for GTD/GTD2/TDC were only asymptotic in nature \cite{gtd,gtd2}.\par
The most relevant to our results are those by \citet{korda-prashanth} in TD(0) and by \citet{gtdmp} in GTD. For the TD(0) case,  diminishing step-sizes $alpha_t=O(\frac{1}{t})^\beta,\beta \in(0,1)$ with PR averaging is showed to exhibit a rate of $O(\frac{1}{t})$ decay for the MSE \cite{korda-prashanth}. In the case of GTD/GTD2 diminishing step-sizes $\alpha_t=O(\frac{1}{\sqrt{t}})$, projection of iterates and PR-averaging leads to a rate of $O(\frac{1}{\sqrt{t}})$ is achieved for the prediction error $\norm{A_P\thh_t-b_P}^2$ with high probability. \citet{gtdmp} also suggests a new version of GTD, based on stochastic mirror prox ideas, called the GTD-Mirror-Prox which also achieves $O(\frac{1}{\sqrt{t}})$ rate for $\norm{\eh_t}$ with high probability under similar step-size choice that was used by them for the GTD.
\paragraph{Our Results} \Cref{th:rate} applies to TD(0)/TDC/GTD/GTD2/GTDMP with CS-PR. Finite time performance of TDC was unkown in prior literature and our work provides a first step by understanding TDC with CS-PR. Further, our results show that the error in the GTD class of algorithms decay at $O(\frac{1}{t})$ rate instead of $O(\frac{1}{\sqrt{t}})$, (without use of projection or mirror maps) which is an improvement. In comparison to the TD(0) results by \citet{korda-prashanth}, \Cref{th:rate} is better in that it provides the bias/variance decomposition. However, it is important to note that \citet{korda-prashanth} handle the Markov noise case which is not dealt with in this paper.

>>>>

\paragraph{SGD for Linear Regression} As mentioned in \Cref{sec:intro}, we were motivated by the ``remarkable'' results obtained by \citet{bach}, where the authors analyze the performance of SGD for the problem of linear regression with quadratic loss. The problem class considered by them belongs to $\P_{\text{PSD},B}$ (see \Cref{def:pclass} ) and hence is weakly admissible with a uniform step-size choice. In order to produce a rate of $\frac{C}{t}$ (where $C>0$ is a problem independent constant) for the bias term \citet{bach} do not rely on admissibility, but instead use the fact that the MSE, $\EE{\norm{\thh_t-\ts}^2_{A_P}}$ for the linear prediction problem is measured in the general quadratic norm with respect to the symmetric positive definite matrix $A_P$ and the fact that the noise is `structured' i.e., the variance is bounded by $R\,A_P$ for some constant $R>0$. At the same time, the bias term decays at a rate $\frac{C'}{t^2}$, where the constant $C'$ contains the factor $(\theta_0-\ts)^\top A^{-1}_P (\theta_0-\ts)$ and is dependent on the condition number.
\paragraph{Our Results:} Analysis of LSA with CS-PR goes back to the work by \citet{polyak-judisky}, wherein they considered the additive noise setting i.e., $A_t=A$ for some deterministic Hurwitz matrix $A\in \R^{\dcd}$.
A key improvement in our paper is that we consider the `multiplicative' noise case, i.e., $A_t$ is a random matrix. To tackle the multiplicative noise we use newer analysis introduced by \citet{bach}. However, since the general LSA setting (with Hurwitz assumption) does not enjoy special structures of the SGD setting of \citet{bach}, we make use of Jordan decomposition and similarity transformations in a critical way to prove our results.
\paragraph{Notation for RL:} We are presented with data in the form of an $i.i.d$ sequence $(\phi_t,\phi'_t,r_t)\in \R^d\times\R^d\times \R$. For a fixed constant $\gamma \in (0,1)$ define  $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$. In what follows, $\mu_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\mu_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\mu_t>0$ is known as \emph{off-policy}.}. The various TD class of algorithms that can be cast as LSAs are given in \Cref{tb:tdalgo}

@@

\label{tb:tdalgo}

@@

\paragraph{Related Work in RL:} The \emph{temporal difference} learning algorithm or simply known as TD(0), is the most basic of the class of TD algorithms. An important shortcoming of TD(0) was its instability in the \emph{off-policy} case, and was successfully mitigated by the \emph{gradient temporal difference} learning GTD algorithm\cite{gtd2}. The GTD was first proposed by \citet{gtd} and its variants namely GTD2 and TDC were proposed later by \citet{gtd2}. However, the initial convergence analysis for GTD/GTD2/TDC were only asymptotic in nature \cite{gtd,gtd2} with diminishing step-sizes.\par
The most relevant to our results are those by \citet{korda-prashanth} in TD(0) and by \citet{gtdmp} in GTD. For the TD(0) case,  diminishing step-sizes $\alpha_t=O(\frac{1}{t})^\beta,\beta \in(0,1)$ with PR averaging is showed to exhibit a rate of $O(\frac{1}{t})$ decay for the MSE when $\beta\ra 1$ \cite{korda-prashanth}. In the case of GTD/GTD2 diminishing step-sizes $\alpha_t=O(\frac{1}{\sqrt{t}})$, projection of iterates and PR-averaging leads to a rate of $O(\frac{1}{\sqrt{t}})$ is achieved for the prediction error $\norm{A_P\thh_t-b_P}^2$ with high probability \cite{gtdmp}. \citet{gtdmp} also suggest a new version of GTD based on stochastic mirror prox ideas, called the GTD-Mirror-Prox which also achieves $O(\frac{1}{\sqrt{t}})$ rate for $\norm{A_P\thh_t-b_P}^2$ with high probability under similar step-size choice that was used by them for the GTD.
\paragraph{Our Results} \Cref{th:rate} applies to TD(0)/TDC/GTD/GTD2/GTDMP with CS-PR since all the TD class of algorithms satisfy the Hurwitz assumption. Finite time performance of TDC was unkown in prior literature and our work provides a first step by understanding TDC with CS-PR. Further, our results show that the error in the GTD class of algorithms decay at $O(\frac{1}{t})$ rate (even without use of projection or mirror maps) instead of $O(\frac{1}{\sqrt{t}})$,  which is an improvement. In comparison to the TD(0) results by \citet{korda-prashanth}, \Cref{th:rate} is better in that it provides the bias/variance decomposition. Further, their results are specific to the TD(0) where $A_P$ is known to be positive definite, and hence cannot be extended in a straightforward manner to GTD class or TDC.
However, it is important to note that \citet{korda-prashanth} handle the Markov noise case which is not dealt with in this paper.

### 2017-05-15 stepsizes.tex
updates

\section{Automatic Tuning of Step-Sizes}
It is straightforwatd to see from \eqref{eq:lsaintro} that $\alpha_t$ cannot be asymptotically increasing. We now present some heuristic arguments in favour of a constant step-size over asymptotically diminishing step-sizes in \eqref{eq:lsaintro}.
It has been observed that when the step-sizes of form $\alpha_t=\frac{c}{t}$ or $\alpha_t=\frac{c}{c+t}$ (for some $c>0$) are used, the MSE, $\EE{\norm{\theta_t-\ts}^2}$, is not robust to the choice of $c>0$ \cite{korda-prashanth,bach-moulines}. In particular only a $O(\frac{1}{t^{\mu c}/2})$ decay can be achieved for the MSE, where $\mu$ is the smallest positive part of the $A_P$ \cite{bach-moulines}. Note that, in the case of LSA with CS-PR, \Cref{th:rate} guarantees a $O(\frac{1}{t})$ rate of decay for the MSE and the problem dependent quantities affect only the constants and not the exponent. Also, in the case of important TD algorithms such as GTD/GTD2/TDC, while the theoretical analysis uses diminishing step-sizes, the experimental results are with a constant step-size or with CS and PR averaging \cite{gtd2,gtdmp}. Independently, \citet{dann} also observe in their experiments that a constant step-size is better than diminishing step-sizes.\par
Motivated by \Cref{th:rate} and also by the usage of constant step-size in practice \cite{dann,gtd2,gtdmp}, we suggest a heuristic algorithm to tune the constant step-size (see \Cref{alg:tuning}).

\begin{comment}
We now argue, in a heuristic manner, as to why constant step-size with PR-averaging might be a principled idea, especially in TD type algorithms. Consider the following LSA with time varying step-sizes $\alpha_t>0$
\begin{align}
\theta_t=\theta_{t-1}+\alpha_t(b_t-A_t\theta_{t-1}).
\end{align}
It is known from asymptotic results by \cite{borkarbook,kushner}\todoch{Check about Kushner} that in order to handle the noise the step-sizes have to be diminishing i.e., $\alpha_t\ra$, unsummable i.e., $\sum_{t \geq 0}\alpha_t=\infty$ and square summable $\sum_{t\geq 0}\alpha_t^2<\infty$. We now look at two specific diminishing step-size sequences, to illustrate the issues that the diminishing step-sizes presents us with. In what follows, we assume that the maximum eigevalue of $\EE{A_t}$ is less that $1$.
\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item \textbf{$\alpha_t=\frac{1}{t}$\footnote{While $\frac{c}{t}$, $c\geq 0$ is more general, it is enough to consider $\frac1t$ by accommodating the multiple $c$ as part of the matrix $A_t$}} is known yield a rate of $\frac{1}{t^{\lambda_{\min}}}$, where $\lambda_{\min}$ is the smallest real part of the eigen values of the matrix $\EE{A_t}$.
\item \textbf{$\alpha_t=\frac{c}{c+t}$} is another example, where the step size decays at a rate $\frac{1}{t/c}$. The rate of decay of error in this case turns out to be $\frac{c^2\sigma_b^2}{t}$, whenever $c>\frac{1}{\lambda_{\min}}$, which can be ensured only when $\lambda_{\min}$ is known.
\end{itemize}
In contrast, in the case of constant step-size with PR-averaging, not knowing the problem instance can result in instability, and when we manage to choose a step-size that results in stable behavior, the rates obtained in \Cref{th:pdrate,cor:as} hold for it. Using this observation, the constant-step size can be set in a more prinicipled manner as showing the pseudocode below.
\end{comment}
\begin{comment}
In \Cref{sec:uniform} we showed a negative result that for the general class of LSAs, it is not possible to pick a fixed uniform step-size that can be used for any instance of the class. Further,
recall from our discussion in \Cref{sec:mainresults} that as $\alpha\ra\alpha_P$ (or $\alpha\ra\alpha_{P_U}$), the MSE blows up and for $\alpha>\alpha_P$ the LSA is unstable because the spectral norm of the random matrix $I-\alpha A_t$ is no longer less that unity. Combining these facts, we conclude that if the step-size is incorrect for a particular instance then we would observe instability, a fact that can be used to reset the step-size to a smaller value, and this procedure can be continued in an iterative fashion to find the right choice of step-size for a given problem. We formalize this idea in the form of a step-size tuning algorithm in \Cref{alg:tuning}
\end{comment}
\begin{algorithm}[H]
\caption{Automatic Tuning of Constant Step-Size}
\begin{algorithmic}[1]
\STATE{Initialize: $\theta_0$, $\alpha=\alpha_{\max}$, $k$, $T$ }
\FOR{$t=1,2,\ldots, $}
\STATE{$\theta_t=\theta_{t-1}+\alpha (b_t-A_t\theta_{t-1}), \thh_t=\thh_{t-1}+\frac{1}{t+1}(\theta_t-\thh_{t-1})$}
\IF{$IsUnstable(\norm{\theta_t},\ldots,\norm{\theta_{(t-kT)\wedge 0}})=1$}
\STATE{$\alpha=\alpha/2$}
\ENDIF
\ENDFOR
\end{algorithmic}
\label{alg:tuning}
\end{algorithm}
In \Cref{alg:tuning} $T>0$ is a time epoch and $k$ is a given integer and $\alpha_{\max}>0$ is the maximum step-size that is allowable. It is easy to show using a Gronwall argument that in \Cref{alg:tuning} $\norm{\theta_t}\leq (1-e^{\beta t})$, where ($\beta>0)$) $\beta<0$ implies (in)stability of iterates. Using this fact, we observe that the sequence $r_i=\frac{\norm{\theta_{(t-kT+iT)\wedge 0}}}{\norm{\theta_{(t-kT+(i-1)T)\wedge 0}}},i=1,\ldots,k$ should be `roughly' (making allowance for the presistent noise) decreasing and converge to $1$. The $IsUnstable()$ routine in \Cref{alg:tuning} can take this sequence of $r_i$s as input, and in the case of instability, the step-size can be scaled down by a factor of $2$ (or any constant factor).
\begin{comment}
In \Cref{alg:tuning} IsUnstable$(\rho_j,j=1,\ldots,i\}$) is a routine whose input is $\norm{\theta_t}$ measured at time instances $k$ apart.
It is easy to show from Gronwall type arguments that the $\norm{\theta_t}\leq (1-exp{\beta t})$, where $\beta>0$ implies stability and $\beta<0$ imples instability. From this Gronwall based inequality, we observe that when the iterates are stable the ratio $\frac{\rho_{k+1}}{\rho_k},k=1,\ldots,i-1$ should be `roughly' decreasing (because there is the iterates are persistently corrupted by noise) and should converge to $1$. This condition on the sequence $\frac{\rho_{k+1}}{\rho_k}$ can be checked in practice with appropriate tolerances.
\end{comment}
\begin{comment}
In order to calculate the rates we make use of the following asymptotic result by \cite{borkarbook}.
\begin{theorem}\label{th:borkar}
Let $\theta_t=\theta_{t-1}+\alpha_t(b_t-A_t\theta_{t-1})$, where $\theta_t,b_t\in\R^d$ and $A_t\in\R^{\dcd}$ that satisfy the conditions in \Cref{assmp:lsa} and $\sum_{t\geq 0}\alpha_t=\infty$, $\sum_{t\geq 0}\alpha^2_t<\infty$. Let $t_{ode}(k)=\eqdef \sum_{i=0}^{k-1}\alpha_n$ and let $\tilde{\theta}(t)$ be the trajectory of the ordinary differential equation $\dot{\theta}(t)=\EE{b_t}-A_P\theta(t)$. Then it follows that
\begin{align*}
\lim_{k\ra\infty}\sup\norm{\tilde{\theta_t(t_{ode}(k))}-\theta_t} \ra 0
\end{align*}
\end{theorem}

For this discussion, let us consider a simple example where $P$ is a distribution with all the mass concentrated at $A_P=\begin{bmatrix}\lambda_{\min} &0\\ 0 &\lambda_{\max}\end{bmatrix}$, $b_t$ is a zero mean $i.i.d$ sequence with variance $\sigma_2_b$.
\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item \textbf{$\alpha_t=\frac{1}{t}$:} In order to ensure stability, we want the eigenvalues of $I-\alpha_t A_P$ to be within unit circle. This restricts the choice of $c$ to be $0<c<\frac{2}{\lambda_{\max}}$. It is straighforward to show that a step-size choice of $\alpha_t=\frac{2}{\lambda_{\max}t}$ will yield a rate of $\frac{1}{t^{2\lambda_{\min}}}$, which can be very bad for small $\lambda_{\min}$.
\item \textbf{}
\end{itemize}
\end{comment}

>>>>

\section{Automatic Tuning of Step-Sizes}
It is straightforward to see from \eqref{eq:lsaintro} that $\alpha_t$ cannot be asymptotically increasing. We now present some heuristic arguments in favour of a constant step-size over asymptotically diminishing step-sizes in \eqref{eq:lsaintro}.
It has been observed that when the step-sizes of form $\alpha_t=\frac{c}{t}$ or $\alpha_t=\frac{c}{c+t}$ (for some $c>0$) are used, the MSE, $\EE{\norm{\theta_t-\ts}^2}$, is not robust to the choice of $c>0$ \cite{korda-prashanth,bach-moulines}. In particular only a $O(\frac{1}{t^{\mu c}/2})$ decay can be achieved for the MSE, where $\mu$ is the smallest positive part of the $A_P$ \cite{bach-moulines}. Note that, in the case of LSA with CS-PR, \Cref{th:rate} guarantees a $O(\frac{1}{t})$ rate of decay for the MSE and the problem dependent quantities affect only the constants and not the exponent. Also, in the case of important TD algorithms such as GTD/GTD2/TDC, while the theoretical analysis uses diminishing step-sizes, the experimental results are with a constant step-size or with CS and PR averaging \cite{gtd2,gtdmp}. Independently, \citet{dann} also observe in their experiments that a constant step-size is better than diminishing step-sizes.\par
We would like to remind that in \Cref{sec:uniform} we showed that weak admissibility might not hold for all problem classes, and hence a uniform choice for the constant step-size might not be possible, However, motivated by \Cref{th:rate} and also by the usage of constant step-size in practice \cite{dann,gtd2,gtdmp}, we suggest a heuristic algorithm to tune the constant step-size (see \Cref{alg:tuning}).
\begin{algorithm}[H]
\caption{Automatic Tuning of Constant Step-Size}
\begin{algorithmic}[1]
\STATE{Initialize: $\theta_0$, $\alpha=\alpha_{\max}$, $k$, $T$ }
\FOR{$t=1,2,\ldots, $}
\STATE{$\theta_t=\theta_{t-1}+\alpha (b_t-A_t\theta_{t-1}), \thh_t=\thh_{t-1}+\frac{1}{t+1}(\theta_t-\thh_{t-1})$}
\IF{$IsUnstable(\norm{\theta_t},\ldots,\norm{\theta_{(t-kT)\wedge 0}})=1$}
\STATE{$\alpha=\alpha/2$}
\ENDIF
\ENDFOR
\end{algorithmic}
\label{alg:tuning}
\end{algorithm}
In \Cref{alg:tuning} $T>0$ is a time epoch and $k$ is a given integer and $\alpha_{\max}>0$ is the maximum step-size that is allowable. It is easy to show using a Gronwall argument that in \Cref{alg:tuning} $\norm{\theta_t}\leq (1-e^{\beta t})$, where ($\beta>0)$) $\beta<0$ implies (in)stability of iterates. Using this fact, we observe that the sequence $r_i=\frac{\norm{\theta_{(t-kT+iT)\wedge 0}}}{\norm{\theta_{(t-kT+(i-1)T)\wedge 0}}},i=1,\ldots,k$ should be `roughly' (making allowance for the persistent noise) decreasing and converge to $1$. The $IsUnstable()$ routine in \Cref{alg:tuning} can take this sequence of $r_i$s as input, and in the case of instability, the step-size can be scaled down by a factor of $2$ (or any constant factor).

### 2017-05-15 uniform.tex
recent updates
updates

\section{Uniform stepsizes}
If $\P$ is weakly admissible, then one can choose a stepsize $\alpha_{\P}>0$ solely based on the knowledge of $\P$ and
conclude that no matter the joint distribution $P$ of $(b_t,A_t)$, as long as the distribution of $P$ is an element of $\P$, the conclusions of \Cref{th:rate} hold. Further, if $\P$ is admissible then the error bound stated in  \cref{maintheorem} becomes independent of the instance. Hence, an interesting question to investigate is whether a given set $\P$ is (weakly) admissible. We consider some reasonable classes of distributions and test whether or not they are (weakly) admissible.
\begin{definition}\label{def:pclass}
\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item For $B>0$, let $\P_B$ be the set of distributions over $\C_B^{d}\times \C_B^{\dcd}$ where for every $P\in \P_B$ is positive definite.
\item  $\P_{\text{PSD},B}$ be such that  $\P^M_{\text{PSD},B}=\{ P^M \in \P^M_B \,:\,  \supp(P^M)\subset \text{PSD} \}\,$ , where PSD denotes the set of positive semi-definite matrices.
\item  $\P_{\text{PD},B}$ be such that  $\P^M_{\text{SD},B}=\{ P^M \in \P^M_B \,:\,  \supp(P^M)\subset \text{PD} \}\,$ , where PD denotes the set of positive definite matrices.
\end{itemize}
\end{definition}
Note that all distributions are a subset of $\P_B$ and in most applications the knowledge of a suitable $B>0$ is available,and by appropriately normalizing the vectors and matrices involved, we may as well assume that $B=1$ without any loss of generality.
\begin{proposition}\label{notwad}
The set $\P_B$ is not weakly admissible.
\end{proposition}
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is weakly admissible
and in particular any $0<\alpha < 2/B$ witnesses this.
\end{proposition}
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is not admissible.
\end{proposition}

@@

\begin{comment}
\begin{proof}
Take any $P\in \P_{\text{PSD}}$ and let $H\sim P$.
Consider the SVD of $H$: $H = U \Lambda U^\top$ where $U$ is orthonormal and $\Lambda$ is diagonal with
nonnegative elements. Note that $\Lambda \preceq B\, \I$ and thus $\Lambda^2 \preceq B \Lambda$.
Then for any $x\in \R^d$, $x^\top H^\top H x = x^\top U \Lambda^2 U^\top x \le B x^\top U \Lambda U^\top x = B x^\top H x$.
Taking expectations we find that $x^\top Q_P x \le B x^\top H_P x$.
Hence, $\rho_\alpha(P) = 2 x^\top H_P x - \alpha x^\top Q_P x \ge (2- \alpha B ) \,x^\top H_P x $.
Thus, for any $\alpha<2/B$, $\rho_\alpha(P)>0$.
\end{proof}
\end{comment}
\todoc[inline]{So this altogether is weaker than what Bach founds. They prove strong admissibility.
I am guessing that for this they use that the loss is special and also that the noise is special.
This would be a good place to somehow incorporate this with a (short?) proof.
}
Thus \Cref{notwad} positive definiteness of $P\in \P_B$ alone is not sufficient for weak admissibility. However, when we impose additional structure in the data in the form of positive semidefiniteness,  we then observe weak admissibility in \Cref{wad}, and at the same time, it is not enough to guarantee admissiblity in \Cref{notad}. Finally, when we impose strucutre in the form of positive definiteness we observe admissibility.
\FloatBarrier
\begin{table}[H]
\begin{tabular}{|c|c|c|c|}\hline
Problem Class & Weak Admissible & Admissible &Example \\ \hline
$\P_B$ &\ding{53} &\ding{53} & RL\\\hline
$\P_{\text{PSD},B}$ &\ding{51} &\ding{53} & SGD for Linear Regression\\\hline
$\P_{\text{PD},B}$ &\ding{51} &\ding{51} & SGD for Linear Regression with regularization\\\hline
\end{tabular}
\end{table}

>>>>

\section{Uniform stepsizes}
If $\P$ is weakly admissible, then one can choose a step-size $\alpha_{\P}>0$ solely based on the knowledge of $\P$ and
conclude that no matter the joint distribution $P$ of $(b_t,A_t)$, as long as the distribution of $P$ is an element of $\P$, the conclusions of \Cref{th:rate} hold. Further, if $\P$ is admissible then the error bound stated in  \cref{maintheorem} becomes independent of the instance. Hence, an interesting question to investigate is whether a given set $\P$ is (weakly) admissible. We consider some reasonable classes of distributions and test whether or not they are (weakly) admissible.
\begin{definition}\label{def:pclass}
\begin{itemize}[leftmargin=*, before = \leavevmode\vspace{-\baselineskip}]
\item For $B>0$, let $\P_B$ be the set of distributions over $\C_B^{d}\times \C_B^{\dcd}$ where for every $P\in \P_B$ is positive definite.
\item  $\P_{\text{PSD},B}$ be such that  $\P^M_{\text{PSD},B}=\{ P^M \in \P^M_B \,:\,  \supp(P^M)\subset \text{PSD} \}\,$ , where PSD denotes the set of positive semi-definite matrices.
\item  $\P_{\text{PD},B}$ be such that  $\P^M_{\text{SD},B}=\{ P^M \in \P^M_B \,:\,  \supp(P^M)\subset \text{PD} \}\,$ , where PD denotes the set of positive definite matrices.
\end{itemize}
\end{definition}
Note that all distributions are a subset of $\P_B$ and in most applications the knowledge of a suitable $B>0$ is available,and by appropriately normalizing the vectors and matrices involved, we may as well assume that $B=1$ without any loss of generality.
\begin{proposition}\label{notwad}
The set $\P_B$ is not weakly admissible.
\end{proposition}
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is weakly admissible
and in particular any $0<\alpha < 2/B$ witnesses this.
\end{proposition}
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is not admissible.
\end{proposition}

@@

\begin{comment}
\begin{proof}
Take any $P\in \P_{\text{PSD}}$ and let $H\sim P$.
Consider the SVD of $H$: $H = U \Lambda U^\top$ where $U$ is orthonormal and $\Lambda$ is diagonal with
nonnegative elements. Note that $\Lambda \preceq B\, \I$ and thus $\Lambda^2 \preceq B \Lambda$.
Then for any $x\in \R^d$, $x^\top H^\top H x = x^\top U \Lambda^2 U^\top x \le B x^\top U \Lambda U^\top x = B x^\top H x$.
Taking expectations we find that $x^\top Q_P x \le B x^\top H_P x$.
Hence, $\rho_\alpha(P) = 2 x^\top H_P x - \alpha x^\top Q_P x \ge (2- \alpha B ) \,x^\top H_P x $.
Thus, for any $\alpha<2/B$, $\rho_\alpha(P)>0$.
\end{proof}
\end{comment}
\todoc[inline]{So this altogether is weaker than what Bach founds. They prove strong admissibility.
I am guessing that for this they use that the loss is special and also that the noise is special.
This would be a good place to somehow incorporate this with a (short?) proof.
}
Thus \Cref{notwad} positive definiteness of $P\in \P_B$ alone is not sufficient for weak admissibility. However, when we impose additional structure in the data in the form of positive semi-definiteness,  we then observe weak admissibility in \Cref{wad}, and at the same time, it is not enough to guarantee admissibility in \Cref{notad}. Finally, when we impose structure in the form of positive definiteness we observe admissibility.
\begin{comment}
\FloatBarrier
\begin{table}[H]
\begin{tabular}{|c|c|c|c|}\hline
Problem Class & Weak Admissible & Admissible &Example \\ \hline
$\P_B$ &\ding{53} &\ding{53} & RL\\\hline
$\P_{\text{PSD},B}$ &\ding{51} &\ding{53} & SGD for Linear Regression\\\hline
$\P_{\text{PD},B}$ &\ding{51} &\ding{51} & SGD for Linear Regression with regularization\\\hline
\end{tabular}
\end{table}
\end{comment}
